---
title: "Untitled"
author: "oushiei"
date: "2023-01-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 連詞の割合

# 

```{r}
suppressPackageStartupMessages({
  library(gridExtra)
  library(ggplot2)
  library(showtext)
  library(quanteda)
  library(quanteda.textstats)
  library(jiebaR)
  library(readtext)
  library(purrr)
  library(tidyverse)
  library(tidytext)
  library(quanteda.textmodels)
  library(quanteda.textplots)
  library(fmsb)})


showtext_auto()
font_add("SourceHanSerif",regular = "/Library/Fonts/SourceHanSerif-Regular.ttc",
         bold="SourceHanSerif-Bold.ttc")
par(family = "SourceHanSerif")
```


#

```{r}
v0 <- readtext("/Users/oushiei/Desktop/论文终稿/finalcode/data/segment",docvarsfrom = "filenames") %>% corpus() %>% tokens(what="fasterword")


```

# 
```{r}
dict <- dictionary(list(并列 = c("和","跟","与","同","及","而","况","况且","何况","乃至"),
                        承接 = c("则","乃","就","而","于是","至于","说到","此外","像","如","一般","比方"),
                        转折 = c("却","但是","然而","而","偏偏","只是","不过","至于","致","不料","岂知"),
                        因果 = c("原来","因为","由于","以便","因此","所以","是故","以致"),
                        选择 = c("或","抑"),
                        假设 = c("若","如果","若是","假如","假使","倘若","要是","譬如"),
                        比较 = c("像","好比","如同","似乎","等于","不如","不及","与其","不如"),
                        让步 = c("虽然","固然","尽管","纵然","即使")))
renshi <- tokens_lookup(v0, dictionary = dict) %>% dfm() 
docnames(renshi) <- docvars(renshi,"docvar1")
renshi_data <- renshi %>% convert(to="data.frame")

renshi_data
write.csv(renshi_data,"/Users/oushiei/Desktop/论文终稿/finalcode/data for print/連詞.csv")
 
```

#

```{r}

df_scaled<-renshi_data %>% select(-doc_id) %>% apply(2, scales::rescale)
df_scaled
rownames(df_scaled) <- renshi_data$doc_id
df_scaled

renshi_data %>% head()
scale_data %>% head()

```


```{r}
create_beautiful_radarchart <- function(data, color = "#00AFBB", 
                                        vlabels = colnames(data), vlcex = 0.7,
                                        caxislabels = NULL, title = NULL, ...){
  radarchart(
    data, axistype = 1,
    # Customize the polygon
    pcol = color, pfcol = scales::alpha(color, 0.5), plwd = 2, plty = 1,
    # Customize the grid
    cglcol = "grey", cglty = 1, cglwd = 0.8,
    # Customize the axis
    axislabcol = "grey", 
    # Variable labels
    vlcex = vlcex, vlabels = vlabels,
    caxislabels = caxislabels, title = title, 
    family = "SourceHanSerif",
    cex = 1.2
  )
}
op <- par(mar = c(1, 2, 2, 2))
# Create the radar charts
create_beautiful_radarchart(
  data = df, caxislabels = c(0, 5, 10, 15, 20),
  color = c("#00AFBB", "#E7B800", "#FC4E07")
)
# Add an horizontal legend
legend(
  x = "bottom", legend = rownames(df[-c(1,2),]), horiz = TRUE,
  bty = "n", pch = 20 , col = c("#00AFBB", "#E7B800", "#FC4E07"),
  text.col = "black", cex = 1, pt.cex = 1.5
  )
```


```{r}
col_max <- apply(df_scaled, 2, max)
col_min <- apply(df_scaled, 2, min)
col_mean <- apply(df_scaled, 2, mean)
col_summary <- t(data.frame(Max = col_max, Min = col_min, Average = col_mean))##变成表格
df_scaled2 <- as.data.frame(rbind(col_summary, df_scaled))
head(df_scaled2)

```

values = c('#3A76A9','#D13021','#FDBF7B','#804B23','#81D8DD'
vlabels: variable labels
vlcex: controls the font size of variable labels #变量标签的大小

pcol: line color #线的颜色
pfcol: fill color
plwd: line width
plty: line types. Can be a numeric vector 1:6 or a character vector c(“solid”, “dashed”, “dotted”, “dotdash”, “longdash”, “twodash”). To remove the line, use plty = 0 or plty = “blank”.
cglcol: line color
cglty: line type
cglwd: line width
axislabcol: color of axis label and numbers. Default is “blue”.
caxislabels: Character vector to be used as labels on the center axis.


```{r}

opar <- par() 
# Define settings for plotting in a 3x4 grid, with appropriate margins:


op <- par(mar = c(1, 1, 1, 1)+0.2)
par(oma = c(1, 2, 1, 1))
par(mfrow = c(1,3))
colors=c("#DE3533", "#0047AB", "#006644",
                               "#10C25B", "#808080","#FF8000")
 
for (i in 4:6) {
  radarchart(
    df_scaled2[c(1:3, i), ],
    pfcol = c("#99999980",NA),
    pcol= c(NA,colors[i-3]), plty = 1, plwd = 2,line=-5,
    title = row.names(df_scaled2)[i],
    vlcex=1.3,calcex=1.2,palcex=2,
    family = "SourceHanSerif", cex.main = 2
  )
 }


for (i in 7:9) {
  radarchart(
    df_scaled2[c(1:3, i), ],
    pfcol = c("#99999980",NA),
    pcol= c(NA,colors[i-3]), plty = 1, plwd = 2,line=-5,
    title = row.names(df_scaled2)[i],
    vlcex=1.3,calcex=1.2,palcex=2,
    family = "SourceHanSerif", cex.main = 2
  )
 }

```

